### 2025-08-05 mixed-models.qmd
20250804 - tweaks
20250804 - leverage multiple cores

modelPredictions_bayesian <- predict(
  object = bayesianMixedModelFit,
  newdata = pointsPerSeason_positionAge_newData,
  re_formula = NA,
  summary = TRUE
)

>>>>

modelPredictions_bayesian <- predict(
  object = bayesianMixedModelFit,
  newdata = pointsPerSeason_positionAge_newData,
  re_formula = NA,
  cores = num_cores
)
